Fitness Adventure: an interactive floor game to maintain body fitness

### 2015-01-28 paper.tex
Add pictures of walkthrough in desired order and combination .. this makes the game understandable only with the pictures. And offers a great possibility to refer to them in the text

>>>>

  % test section
  \begin{figure}[!htb]
    \centering
    \includegraphics[width=0.32\linewidth]{Image_4.jpg}
    \includegraphics[width=0.32\linewidth]{Image_5.jpg}
    \includegraphics[width=0.32\linewidth]{Image_1.jpg}
    \caption{(left) Enter the floor to start the game. (middle) Step on the spot to move through the world. (right) Jump over fallen trees.}
  \end{figure}

  \begin{figure}[!htb]
    \centering
    \includegraphics[width=0.32\linewidth]{Image_7.jpg}
    \includegraphics[width=0.32\linewidth]{Image_2.jpg}
    \includegraphics[width=0.32\linewidth]{Image_8.jpg}
    \caption{(left) Reach the sea. (middle) Hold on ice floes to get over. (right) Ice floes will sink, so always switch to a stable one.}
  \end{figure}

  \begin{figure}[!htb]
    \centering
    \includegraphics[width=0.32\linewidth]{Image_6.jpg}
    \includegraphics[width=0.32\linewidth]{Image_6.jpg}
    \includegraphics[width=0.32\linewidth]{Image_6.jpg}
    \caption{Penalty: (left) Hitting a tree brings 10s time penalty. (middle) Illustration from the side. (right) Touching the water does as well.}
  \end{figure}

  \begin{figure}[!htb]
    \centering
    \includegraphics[width=0.32\linewidth]{Image_9.jpg}
    \includegraphics[width=0.32\linewidth]{Image_3.jpg}
    \includegraphics[width=0.32\linewidth]{Image_10.jpg}
    \caption{(left) Reach a broken bridge. (middle) Get the wooden planks. (right) Build up the bridge to cross the water. (Remember penalty)}
  \end{figure}
  % end test section
